{
	\begin{article}{Officers}
		\item \textbf{President}
		
		Duties shall include:
		\begin{enumerate}
			\item To call for and preside over all general meetings.
			\item To delegate duties and temporary officer positions to other members when necessary.
			\item To act as a mediator between members or non-member affiliated persons of this organization when necessary.
			\item To act as mediator with other organizations on or off campus, including the Student Government Association, when necessary. 
			\item To act as mediator between this organization and the faculty, staff, or administration of Grove City College when necessary.
		\end{enumerate}
		\item \textbf{Vice President}
		
		Duties shall include:
		\begin{enumerate}
			\item To assume the duties of the President in the event of his absence.
			\item To be responsible for organizing and carrying out any activities that do not occur on a weekly or bi-weekly basis.
			\item To be responsible for organizing and carrying out membership drives.
			\item To act as induction chairman for the taking of new members.
		\end{enumerate}
		\item \textbf{Secretary}
		
		Duties shall include:
		\begin{enumerate}
			\item To record the minutes of all regular meetings.
			\item To notify all members of upcoming regular meetings and events.
			\item To be responsible for appending all amendments to the constitution.
			\item To be responsible for all outside correspondence including, but not limited to maintaining contact with alumni, other campus organizations, and persons within the Grove City College body.
		\end{enumerate}
		\item \textbf{Treasurer}
		
		Duties shall include:
		\begin{enumerate}
			\item To be responsible for all monies entering or leaving the organization.
			\item To update the roster of members at the first meeting of each semester or when necessary.
			\item To act as a mediator between this organization and the Financial Services Office.
			\item To assist the President in the acquisition of funds from the Student Government Association whenever the Executive Committee deems necessary.
			\item To collaborate with the Sergeant at Arms for the procurement of equipment for the organizational library.
		\end{enumerate}
		\item \textbf{Sergeant at Arms}
		
		Duties shall include:
		\begin{enumerate}
			\item To be responsible for any materials belonging to the organizational library. This includes the usage of any materials therein by other members.
			\item To collaborate with the Treasurer for the procurement of equipment for the organizational library.
			\item To assist the President in maintaining order during the weekly meetings and other activities.
			\item To assist the President in acting as a mediator between members or non-member affiliated persons of this organization when necessary.
			\item To begin the weekly meetings on time as set forth in Article I of the By-Laws.
		\end{enumerate}
	\end{article}
}