{
\begin{article}{Officers}
	\item The officers of The Order of Saint George include the following positions in order of authority and succession.

	\item \textbf{President}

	Duties shall include:
	\begin{enumerate}
		\item To call for and preside over all general meetings.
		\item To delegate duties to other members when necessary.
		\item To act as a mediator between members or non-member affiliated persons of this organization when necessary.
		\item To act as mediator with other organizations on or off campus, including the Student Government Association, when necessary.
		\item To act as mediator between this organization and the faculty, staff, or administration of Grove City College when necessary.
	\end{enumerate}
	\item \textbf{Vice President}

	Duties shall include:
	\begin{enumerate}
		\item To assume the duties of the President in the event of his/her absence.
		\item To be responsible for organizing and carrying out membership drives.
		\item To act as an administrator for all Order of Saint George accounts.
	\end{enumerate}
	\item \textbf{Secretary}

	Duties shall include:
	\begin{enumerate}
		\item To record the minutes of all regular meetings.
		\item To notify all members of upcoming regular meetings and events.
		\item To be responsible for appending all amendments to the constitution.
		\item To be responsible for all outside correspondence including, but not limited to maintaining contact with alumni, other campus organizations, and persons within the Grove City College body.
	\end{enumerate}
	\item \textbf{Treasurer}

	Duties shall include:
	\begin{enumerate}
		\item To be responsible for all monies entering or leaving the organization.
		\item To update the roster of members at the first meeting of each semester or when necessary.
		\item To act as an envoy between this organization and the Financial Services Office.
		\item To assist the President in the acquisition of funds from the Student Government Association whenever the Executive Committee deems necessary.
		\item To collaborate with the Sergeant at Arms for the procurement of equipment for the organizational library.
	\end{enumerate}
	\item \textbf{Sergeant at Arms}

	Duties shall include:
	\begin{enumerate}
		\item To be responsible for any materials belonging to the organizational library. This includes the usage of any materials therein by other members.
		\item To collaborate with the Treasurer for the procurement of equipment for the organizational library.
		\item To assist the President in maintaining order during the weekly meetings and other activities.
		\item To assist the President in acting as a mediator between members or non-member affiliated persons of this organization when necessary.
		\item To begin the weekly meetings on time as set forth in \refByLaws{1}.
	\end{enumerate}
	\item If any member of the Executive Committee is temporarily or permanently removed from his/her position by any means, the succession of his/her position shall fall to the next officer in the order of hierarchy.  This shall remain until the next meeting called by the President, in which a candidate for replacement shall be chosen from the pool of members present and will be voted upon by all attending members.  If an emergency meeting is needed to complete this task prior to the initial payment of dues at the start of the fall semester, all attendees, not limited to members may vote.  The replacement officer shall serve the remainder of the departing officer's term.If the replacement officer elected during the emergency meeting is part of the Executive Committee, this officer shall be notified of the Executive Account's password.
	\item \textbf{Temporary Officer Positions}

	Duties shall be set forth by the Executive Committee and agreed upon by a quorum.

	Temporary officer positions shall be instated by the Executive Committee at its discretion and one's appointment must be accepted by the recipient to take effect.  Upon acceptance, the recipient shall perform to the best of his/her ability the duties of the position agreed upon by the recipient and the Executive Committee.  The recipient shall serve for the remainder of the current election cycle or until the position is terminated.  Temporary officer positions may be renewed at the time of the annual officer elections.

	Temporary officer positions may be terminated by the Executive Committee at any time deemed necessary.  A temporary officer will lose his/her position when he/she is no longer listed on the roster, and if a replacement is not decided upon, the position will be removed.
	\item \textbf{Mascot}

	Any person, place, thing, or idea may be the Mascot.  Nominations for Mascot will be held at the time of elections.  If the Mascot is deemed a threat to the organization as a whole or to its members, the Mascot will be removed through a process paralleling the one outlined in Section 3 of \refByLaws{2} even if the Mascot is not a member.
\end{article}
}