{
\begin{article}{Elections}
	\item All members in good standing with both the college and this organization are eligible to be nominated.
	\item Candidates for office shall be nominated one weekly meeting prior to the time of the election. The presiding officer of each position shall inform those nominated for his/her position of the duties and responsibilities maintained by that officer.
	\item Officers shall be elected at the last meeting of the fall semester.
	\item Newly elected officers will take office the first meeting of the spring semester.
	\item Officers will be elected by a vote of a quorum.
	\item After the election and before the newly elected officers take office, the Alumni Representative, Advisor, or a previous member of the Executive Committee shall be responsible for ensuring the understanding of the duties and responsibilities of the Executive Committee by each of the newly elected officers during a private meeting. Any other necessary information shall be stated during this private meeting.
	\item Between the times of election and inauguration, the Executive Committee elect shall collectively decide on a new password for the Executive Account. Upon inauguration, the prior Executive Committee shall inform the new Executive Committee of the prior password to the Executive Account, and the new Executive Committee shall then change the Executive Account’s password to the one they have agreed upon. This password shall not be further changed without the consent of all officers in the Executive Committee.
\end{article}
}